---
title: "SDS315_HW9"
author: "William Zuo"
date: "2025-04-18"
output:
  html_document:
    toc: true
    toc_float: true
  pdf_document:
    toc: true
---

```{r global_options, include=FALSE}
#needed packages:
library(tidyverse)
library(dplyr)
library(mosaic)
library(moderndive)
library(effectsize)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
```

# **Introduction**

My name is William Zuo and my EID is wcz82. This is where my results and solutions are contained. Here is the link to my GitHub repository containing my R code for this assignment: https://github.com/black-bird5/SDS315_HW9. 

# **Problem 1**

```{r, echo=FALSE}
solder <- read.csv("solder.csv")
```

### **Part A**

```{r, echo=FALSE}
ggplot(solder) +
  geom_boxplot(aes(x = Opening, y = skips)) +
  labs(title = "Solder Opening Size Vs. Number of Skips",
       x = "Solder Opening Size",
       y = "Number of Skips")

ggplot(solder) +
  geom_boxplot(aes(x = Solder, y = skips)) +
  labs(title = "Solder Thickness Vs. Number of Skips",
       x = "Solder Thickness",
       y = "Number of Skips")
```

### **Part B**

```{r, echo=FALSE}
skips_model <- lm(skips ~ Opening + Solder + Opening:Solder, data = solder)
get_regression_table(skips_model, conf.level = 0.95, digits=2)
```

### **Part C**

Intercept - The estimated number of skips when the solder opening size is large and solder thickness is thick is 0.39.

Opening: M - The estimated change in the number of skips when moving from a large to a medium solder opening size, while keeping solder thickness as thick, is 2.41.

Opening: S - The estimated change in the number of skips when moving from a large to a small solder opening size, while keeping solder thickness as thick, is 5.13.

Solder: Thin - The estimated change in the number of skips when moving from a thick to a thin solder thickness, while keeping solder opening size as large, is 2.28.

Opening: M:SolderThin - The interaction when moving from a large to a medium solder opening size and changing the solder thickness from thick to thin causes an estimated change of -0.74 in the number of skips.

Opening: S:SolderThin - The interaction when moving from a large to a small solder opening size and changing the solder thickness from thick to thin causes an estimated change of 9.65 in the number of skips.

### **Part D**

Based on the regression model, I would recommend a solder opening size of large and a solder thickness of thick to minimize the number of skips in the manufacturing process, since every other every possible combination of solder opening size and solder thickness will have a positive coefficient, even including interaction effects, thus increasing the number of skips.

# **Problem 2**

```{r, echo=FALSE}
groceries <- read.csv("groceries.csv")
```

### **Part A**

```{r, echo=FALSE}
avg_store_price <- summarize(group_by(groceries, Store), mean_price = mean(Price))

ggplot(avg_store_price) + 
  geom_col(aes(x = reorder(Store, mean_price), y = mean_price)) +
  coord_flip() + 
  labs(title = "Average Product Price by Store",
       x = "Store",
       y = "Average Price of Products ($)",
       caption = "This graph shows the average price of products across a variety of stores")
```

### **Part B**

```{r, echo=FALSE}
product_count <- summarize(group_by(groceries, Product), store_count = n())

ggplot(product_count) + 
  geom_col(aes(x = store_count, y = reorder(Product, store_count))) + 
  labs(title = "Availability of Products Across Stores",
       x = "Number of Stores Selling Product",
       y = "Product",
       caption = "This graph shows how many stores are selling certain products")
```

### **Part C**

```{r, echo=FALSE}
type_model <- lm(Price ~ Product + Type, data = groceries)
get_regression_table(type_model, conf.level = 0.95, digits=2)
```

Compared with ordinary grocery stores (like Albertsons, HEB, or Krogers), convenience stores charge somewhere between 0.41 and 0.92 dollars more for the same product.

### **Part D**

```{r, echo=FALSE}
store_model <- lm(Price ~ Product + Store, data = groceries)
get_regression_table(store_model, conf.level = 0.95, digits=2)
```

The 2 stores that seem to charge the lowest prices when comparing the same product are Walmart and Kroger Fresh Fare. The 2 stores that seem to charge the highest prices when comparing the same product are Whole Foods and Wheatsville Food Co-Op. 

### **Part E**

From the regression model constructed in part D, it seems that Central Market charges more than HEB for the same product. While we can estimate that Central Market charges 0.57 dollars less for the same product when compared to Albertsons, H-E-B charges 0.65 dollars less. From this, we can conclude from our estimate that Central Market charges 0.08 dollars more for the same product compared to H-E-B. However, this price difference is smaller compared to different store types, such as convenience stores and high-end grocery stores. 

### **Part F**

```{r, echo=FALSE}
groceries <- mutate(groceries, Income10K = Income / 10000)
income10k_model <- lm(Price ~ Product + Income10K, data = groceries)
get_regression_table(income10k_model)
standardize_parameters(income10k_model)
```

Based on the sign of the Income10K coefficient, consumers in poorer ZIP codes seem to pay more for the same product, on average. This is because the coefficient is -0.014, which means that for every 10K decrease in income, prices will increase by 0.014 dollars. 

A one-standard deviation increase in the income of a ZIP code seems to be associated with a -0.03 standard-deviation change in the price that consumers in that ZIP code expect to pay for the same product.

# **Problem 3**

### **Statement A**

A. ZIP codes with a higher percentage of minority residents tend to have more FAIR policies per 100 housing units.

TRUE

Figure A1 shows a positive correlation between the percentage of minority residents and the number of FAIR policies per 100 housing units. Additionally, model_A shows that the coefficient of minority on policies is 0.014 with a 95% confidence interval that does not contain 0, which means for every percent increase in minority residents in a ZIP code there will also be 0.014 more FAIR policies per 100 housing units and that we are 95% confident the true coefficient of minority is not 0.

### **Statement B**

B. The evidence suggests an interaction effect between minority percentage and the age of the housing stock in the way that these two variables are related to the number of FAIR policies in a ZIP code.

UNDECIDABLE

Neither figure B1 nor model_B tested for the interaction between minority percentage and the age of the housing stock on the number of FAIR policies in a ZIP code. The evidence does not rule out the possibility that there is an interaction effect, but it does not show it either. 

### **Statement C**

C. The relationship between minority percentage and number of FAIR policies per 100 housing units is stronger in high-fire-risk ZIP codes than in low-fire-risk ZIP codes.

FALSE

model_C shows us that, while minority:fire_riskLow has a coefficient of -0.001, it also has a 95% confidence interval of [-0.012, 0.01]. This means that we cannot conclude with 95% confidence that the relationship between minority percentage and number of FAIR policies per 100 housing units is stronger in high-fire-risk ZIP codes than in low-fire-risk ZIP codes, since there is a possibility that the true coefficient of minority:fire_riskLow is 0, meaning relationship strength is the same regardless of fire risk, or that it is positive, meaning the relationship is actually stronger in low fire risk ZIP codes. 

### **Statement D**

D. Even without controlling for any other variables, income “explains away” all the association between minority percentage and FAIR policy uptake.

FALSE

model_D2 shows us that, even after controlling for income, minority still has a coefficient of 0.01, with a 95% confidence interval that does not contain 0. Since the coefficient is not 0 and we are 95% confident the true coefficient of minority is not 0, we can conclude that income does not explain away ALL the association between minority percentage and the number of FAIR policies per 100 housing units. 

### **Statement E**

E. Minority percentage and number of FAIR policies are still associated at the ZIP code level, even after controlling for income, fire risk, and housing age.

TRUE

Looking at model_E, we can see that, even after controlling for income, fire risk, and housing age, minority still has a coefficient of 0.008 and a 95% confidence interval that does not contain 0. This means that for every 1% increase in minority residence, the number of FAIR policies per 100 housing units will increase by 0.008, IN VIRTUE OF that increase in minority percentage, and  we are 95% confident the true coefficient of minority is not 0
